A comparative analysis of AquaMaps and IUCN species distribution maps

### 2015-12-14 R/data_explore_global_maps.Rmd
continuing to work on manuscript.  Added figure showing difference in spatial coverage

if(!file.exists(am_all_rast_file)) {
  am_spp_cells_big <- fread(file.path(dir_am_data, 'hcaf_sp_native_trunc.csv')) %>%
    as.data.frame(stringsAsFactors = FALSE)

@@

  writeRaster(all_am_map, filename = am_all_rast_file, overwrite = TRUE)

@@

all_iucn_rast_file   <- 'rasters/am_all_rast.tif'

if(!file.exists(iucn_all_rast_file)) {
  iucn_cells_file    <- file.path(dir_data_iucn, 'iucn_cells_2015.csv')
  iucn_spp_cells_all <- fread(iucn_cells_file) %>%
        as.data.frame(stringsAsFactors = FALSE)

@@

} else {
  all_iucn_map   <- raster(iucn_all_rast_file)
}

@@

am_map_max <- max(all_am_map, na.rm = TRUE)
all_am_pct_map <- all_am_map/am_map_max

iucn_map_max <- max(all_iucn_map, na.rm = TRUE)
all_iucn_pct_map <- all_iucn_map/iucn_map_max

@@

### plot maps with distributions as percentages.  Should it be 0 - 1, or 
### 0 - max value?
levelplot(am_sp_pct_map, par.settings = myTheme, 
          main = 'Aquamaps Dataset pct', 
          colorkey = list( at = seq(0, 1, length = 15)))
levelplot(iucn_sp_pct_map, par.settings = myTheme, 
          main = 'IUCN Dataset pct', 
          colorkey = list(at = seq(0, 1, length = 15)))
### this is the difference one. Should it be min value to max value?
levelplot(diff_pct_map, par.settings = myTheme, 
          main = 'IUCN pct - AM pct', 
          colorkey = list(at = seq(-1, 1, length = 15)))

### Do similar, but with the full aquamaps list (should also do this
### against the full IUCN list...)
all_am_pct_map <- subs(loiczid_raster, all[ , c('loiczid', 'all_pct')], 
                   by = 'loiczid', 
                   which = 'all_pct', 
                   subsWithNA = TRUE)

diff_pct_map2    <- iucn_sp_pct_map - all_am_pct_map
levelplot(all_am_pct_map, par.settings = myTheme, main = 'Entire Aquamaps Dataset, pct')
levelplot(diff_pct_map2, par.settings = myTheme, main = 'iucn (overlap only) - aquamaps (all)')

>>>>

if(!file.exists(all_am_rast_file)) {
  am_spp_cells_big <- fread(file.path(dir_am_data, 'hcaf_sp_native_trunc.csv')) %>%
    as.data.frame(stringsAsFactors = FALSE)

@@

  writeRaster(all_am_map, filename = all_am_rast_file, overwrite = TRUE)

@@

all_iucn_rast_file   <- 'rasters/iucn_all_rast.tif'

if(!file.exists(all_iucn_rast_file)) {
  iucn_cells_file    <- file.path(dir_data_iucn, 'iucn_cells_2015.csv')
  iucn_spp_cells_all <- fread(iucn_cells_file) %>%
        as.data.frame(stringsAsFactors = FALSE)

@@

} else {
  all_iucn_map   <- raster(all_iucn_rast_file)
}

@@

am_map_max <- maxValue(all_am_map)
all_am_pct_map <- all_am_map/am_map_max

iucn_map_max <- maxValue(all_iucn_map)
all_iucn_pct_map <- all_iucn_map/iucn_map_max

@@

### plot maps with distributions as percentages.  Should it be 0 - 1, or 
### 0 - max value?
levelplot(all_am_pct_map, par.settings = myTheme, 
          main = 'Aquamaps Dataset percent of max', 
          colorkey = list( at = seq(0, 1, length = 15)))
levelplot(all_iucn_pct_map, par.settings = myTheme, 
          main = 'IUCN Dataset percent of max', 
          colorkey = list(at = seq(0, 1, length = 15)))
### this is the difference one. Should it be min value to max value?
levelplot(diff_pct_map, par.settings = myTheme, 
          main = 'Difference: AquaMaps - IUCN by percent', 
          colorkey = list(at = seq(-1, 1, length = 15)))

### 2015-12-14 ms_outline.Rmd
continuing to work on manuscript.  Added figure showing difference in spatial coverage

___Note that these level plots show the mean() of the cell value for each row and each column.___  For a difference plot, maybe there's another function that can show us that?

>>>>

![](figures/all_am-all_iucn_map.png)

___Note: I believe these level plots show the mean() of the cell value for each row and each column.___  For a difference plot, maybe there's another function that can show us that?
